---
title: "Flipped Assignment 18"
author: "Group 5"
date: "2022/4/26"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MASS)
library(tibble)
library(car)
library(dplyr)
library(ggplot2)
```

## Input Data
```{r setup1, echo=TRUE}
setwd('G:/OneDrive - Texas Tech University/IE 5344 Statistical Data Analysis/Flipped Assignment 18')
data <- read.csv('data-13-5.csv', header = TRUE)
```

## Part a.
```{r 1, echo=TRUE}
fit <- glm(y~., data, family = binomial(link='logit'))
summary(fit)
```

So, $logit = -7.047 + 7.382e-5x_1 + 9.879e-01x_2$.

## Part b.

The null deviance is 27.726 and the residual deviance is 21.082.

```{r 2, echo=TRUE}
qchisq(0.95,1)
```

This model is significant because $3.841459 < 6.644$.

## Part c.
```{r 3, echo=TRUE}
O1 <- exp(1000*7.382e-5)
O2 <- exp(9.879e-01)
O1
O2
```
For the total family income's increase by $1000$ dollar, the estimated probability of buying a new car in next 6 months increases by about 7.7%.

For the age of oldest car's increase by 1 year, the estimated probability of buying a new car in next 6 months increases by about 168.56%.

## Part d.
```{r 4, echo=TRUE}
predict(fit, data.frame(x1 = c(45000), x2 = c(5)), type='response')
```

The estimated probability that a family with an income of $45,000 and a car that is 5 years old will purchase a new vehicle in the next 6 months is 77.10%.